### 2024-06-10 paper.tex
add erc

\subsection*{Acknowledgements}
SA and LPMK acknowledge funding by the Klaus Tschira Foundation (project 00.022.2019).
LPMK, MMB, LK, SC, and AMV acknowledge funding from the European Commission via ERC grant 771376 (to AMV), from the DFG via SFB 873, and from the DKFZ.
We thank Alexey Uvarovskii for code refactoring and helpful suggestions on the source code.

@@

LPMK and SA conceived and worked out the method.
LPKM wrote the software package, with contributions from MMB (differential methylation functionality) and LKü.
LPMK, SO and LKü prepared the use-case demonstrations and performed the benchmarks.
SC and AMV contributed experimental data and biological expertise.
LPMK, AMV and SA contributed supervision and project management.
LPMK and SA wrote the paper.

>>>>

\subsection*{Acknowledgements}
SA and LPMK acknowledge funding by the Klaus Tschira Foundation (project 00.022.2019).
LPMK, MMB, LK, SC, and AMV acknowledge funding from the European Commission via ERC grants 771376 (to AMV) and 101071786 (to AMV and SA), from the DFG via SFB 873, and from the DKFZ.
We thank Alexey Uvarovskii for code refactoring and helpful suggestions on the source code.

@@

LPMK, SA and AMV conceived the project and LPKM and SA worked out the method.
LPKM wrote the software package, with contributions from MMB (differential methylation functionality) and LKü.
LPMK, SO, LKü and MMB prepared the use-case demonstrations and performed the benchmarks.
SC and AMV contributed experimental data and biological expertise.
LPMK, AMV and SA contributed supervision and project management.
LPMK and SA wrote the paper.
